Structural Divergence Analysis

### 2016-09-29 OUT/analysis-structure.Rmd
cambios 29-09-2016

```{r load_libraries}
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```
# Introduction
We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.

@@

```{r set_file_names}
## input and pre-processing of data
# set up input filenames

reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

```{r set_reference_protein}
## which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
```

We use the `r enm` Elastic Network Model with `R0 =` `r R0` for the `r family` family. 
We use as reference for the ENM the protein with pdb code `r reference`.
The `r family` family consists of the following proteins:

```{r set_experimental_protein_names}
## Experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

@@

```{r set_up_site_info, eval = T}

## read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ",")[1:151, ]

## add info to site.info
d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))

## Define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
levels(d$shell) = seq(length(levels(d$shell))) - 1 # rename shell levels
site.info = merge(site.info, d, by = "site")

## Read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA, CN)
names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))

## Add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

@@

```{r read_experimental_data}
# read experimental data
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
dri2.exp = dri2.exp[, site]
rownames(dri2.exp) = protein.exp

@@

energy.exp = read.csv(energy.exp.fname, header = T)
rownames(energy.exp) = protein.exp

@@

```{r read_and_set_data_mut}
# read simulated data

dri2.mut = read.csv(dri2.mut.fname, header = T)
site = site.info$site
dri2.mut = dri2.mut[, site]
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

@@

```{r read_and_set_data_strong}
# read simulated data

dri2.strong = read.csv(dri2.strong.fname, header = T)
site = site.info$site
dri2.strong = dri2.strong[, site]
rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")

@@

```{r prepare-site-data}
# Prepare my data.frame
# rows of dri2 are proteins, columns are sites

@@

```{r mean-z-RSD-vs-site}
# Comparison of z.RSD profiles annotated with functional information (reported active sites).
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

# dat.with.means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

@@

plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM$min.da.ca[1:151])
plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM$min.da.CM[1:151])

@@

# Plot separate and comparative plots
p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet
#p + theme(legend.position = "bottom", legend.title = element_blank())
p + theme(legend.position = "bottom")

@@

VAL107 and its neighbors (including site 32) are more structurally conserved than predicted.

@@

r.exp.mut = cor(dat.exp$mean.z.RSD, dat.mut$mean.z.RSD)
r.exp.strong = cor(dat.exp$mean.z.RSD, dat.strong$mean.z.RSD)
r.mut.strong = cor(dat.mut$mean.z.RSD, dat.strong$mean.z.RSD)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)
write.csv(dat, "structure-comparison-profiles.csv")

# Write pdb files for MSDi.

  pdb = ReadCA(reference.pdb.fname, chain.p.ref)$xyz

  mean.exp.z.RSD.pdb <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
  write.pdb(xyz = c(pdb), b = mean.exp.z.RSD.pdb, file = paste(p.ref, "_exp.pdb", sep = ""))

  mean.mut.z.RSD.pdb <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
  write.pdb(xyz = c(pdb), b = mean.mut.z.RSD.pdb, file = paste(p.ref, "_mut.pdb", sep = ""))

  mean.strong.z.RSD.pdb <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
  write.pdb(xyz = c(pdb), b = mean.strong.z.RSD.pdb, file = paste(p.ref, "_strong.pdb", sep = ""))
```

@@

# Prepare modeComparison.strong
tPn.strong = as.data.frame(t(as.matrix(Pn.strong)))
tPn.strong = cbind(data.frame("mode" = mode), tPn.strong)
Pn.strong.long = melt(tPn.strong, "mode", variable.name = "protein", value.name = "Pn")

@@

# Prepare modeComparison.mut
tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
Pn.mut.long = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")

@@

# Prepare modeComparison.exp
tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
Pn.exp.long = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")

@@

# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
modeComparison.exp <- na.omit(modeComparison.exp)
modeComparison.strong <- na.omit(modeComparison.strong)
modeComparison.mut <- na.omit(modeComparison.mut)

@@

```{r}
## Quantile regression

# fit median and quantiles to simulated data and add them to data.frames
fit.strong.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.strong, method = "fn")
fit.strong.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.strong, method = "fn")
fit.strong.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.strong, method = "fn")
modeComparison.strong$rq.5 = fit.strong.rq.5$fitted.values
modeComparison.strong$rq.05 = fit.strong.rq.05$fitted.values
modeComparison.strong$rq.95 = fit.strong.rq.95$fitted.values

# fit median and quantiles to simulated data and add them to data.frames
fit.mut.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.mut, method = "fn")
fit.mut.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.mut, method = "fn")
fit.mut.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.mut, method = "fn")
modeComparison.mut$rq.5 = fit.mut.rq.5$fitted.values
modeComparison.mut$rq.05 = fit.mut.rq.05$fitted.values
modeComparison.mut$rq.95 = fit.mut.rq.95$fitted.values

# fit median and quantiles to experimental data
fit.exp.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.exp, method = "fn")
fit.exp.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.exp, method = "fn")
fit.exp.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.exp, method = "fn")
modeComparison.exp$rq.5 = fit.exp.rq.5$fitted.values
modeComparison.exp$rq.05 = fit.exp.rq.05$fitted.values
modeComparison.exp$rq.95 = fit.exp.rq.95$fitted.values

# put simulated and experimental data together

@@

```{r Pn-vs-mode-energy,cache = 2}
# Plot Pn vs energy
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,2.5)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,1))

p.facet = p + facet_grid(dataset~.,switch="y") + theme(legend.position="none")
p.facet %+% subset(dat,dataset =="exp")
p.facet %+% subset(dat,dataset == "mut")
p.facet %+% subset(dat,dataset == "mut+sel")
p.facet
p + theme(legend.position = "bottom")

@@

```{r}
dat = modeComparison.all.datasets
#dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

@@

r.exp.mut = cor(dat.exp$Pn.median, dat.mut$Pn.median)
r.exp.strong = cor(dat.exp$Pn.median, dat.strong$Pn.median)
r.mut.strong = cor(dat.mut$Pn.median, dat.strong$Pn.median)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)

[//]: Write output for further analysis with other programs

```{r write-data-to-output}
write.csv(siteComparison.exp, "site-structure-comparison-exp.csv",row.names=F)
write.csv(modeComparison.exp, "mode-structure-comparison-exp.csv",row.names=F)
```

>>>>

```{r load_libraries}
# Load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# Source functions
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```

# Introduction
We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.

@@

```{r set_file_names}
# input and pre-processing of data

## set up input filenames
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

```{r set_reference_protein}
# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
```

We use the ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
``` Elastic Network Model with `R0 =` `r R0` for the `r family` family. 
We use as reference for the ENM the protein with pdb code `r reference`.
The `r family` family consists of the following proteins:

```{r set_experimental_protein_names}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

@@

```{r set_up_site_info, eval = T}
# read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ",")

# add info to site.info
d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))

# define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
levels(d$shell) = seq(length(levels(d$shell))) - 1 # rename shell levels
site.info = merge(site.info, d, by = "site")

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA, CN)
names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))

# add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

@@

```{r read_experimental_data}

# read experimental data
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
dri2.exp = dri2.exp[, site]
rownames(dri2.exp) = protein.exp

@@

energy.exp = read.csv(energy.exp.fname, header = T)
rownames(energy.exp) = protein.exp
```

@@

```{r read_and_set_data_mut}

# read simulated data
dri2.mut = read.csv(dri2.mut.fname, header = T)
site = site.info$site
dri2.mut = dri2.mut[, site]
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

@@

```{r read_and_set_data_strong}

# read simulated data
dri2.strong = read.csv(dri2.strong.fname, header = T)
site = site.info$site
dri2.strong = dri2.strong[, site]
rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")

@@

```{r prepare-site-data}
# prepare my data.frame
# note: rows of dri2 are proteins, columns are sites

@@

```{r mean-z-RSD-vs-site}
# comparison of z.RSD profiles annotated with functional information (reported active sites).
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

## dat.with.means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

@@

plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM$min.da.ca)
plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM$min.da.CM)

@@

## plot separate and comparative plots
p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet

#p + theme(legend.position = "bottom", legend.title = element_blank())

p + theme(legend.position = "bottom")

@@

@@

r.exp.mut = cor(dat.exp$mean.z.RSD, dat.mut$mean.z.RSD)
r.exp.strong = cor(dat.exp$mean.z.RSD, dat.strong$mean.z.RSD)
r.mut.strong = cor(dat.mut$mean.z.RSD, dat.strong$mean.z.RSD)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)
write.csv(dat, "structure-comparison-profiles.csv")
```

```{r write-pdb-files}
# write pdb files with mean.z.RSDi as b-factor for building images

## read pdb CAs
pdb.xyz.ca = ReadCA(reference.pdb.fname, chain.p.ref)$xyz

## experimental
exp.mean.z.RSD.vec <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file = paste(p.ref, "_exp.pdb", sep = ""))

## mut
mut.mean.z.RSD.vec <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = paste(p.ref, "_mut.pdb", sep = ""))

## mut + sel / strong
strong.mean.z.RSD.vec <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = paste(p.ref, "_strong.pdb", sep = ""))
```

@@

# prepare modeComparison.strong
tPn.strong = as.data.frame(t(as.matrix(Pn.strong)))
tPn.strong = cbind(data.frame("mode" = mode), tPn.strong)
Pn.strong.long = melt(tPn.strong, "mode", variable.name = "protein", value.name = "Pn")

@@

# prepare modeComparison.mut
tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
Pn.mut.long = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")

@@

# prepare modeComparison.exp
tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
Pn.exp.long = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")

@@

# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
# print("Warning: modeComparison <- na.omit(modeComparison)")

modeComparison.exp <- na.omit(modeComparison.exp)
modeComparison.strong <- na.omit(modeComparison.strong)
modeComparison.mut <- na.omit(modeComparison.mut)
```

@@

```{r}
# quantile regression

## fit median and quantiles to simulated data and add them to data.frames
fit.strong.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.strong, method = "fn")
fit.strong.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.strong, method = "fn")
fit.strong.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.strong, method = "fn")

modeComparison.strong$rq.5 = fit.strong.rq.5$fitted.values
modeComparison.strong$rq.05 = fit.strong.rq.05$fitted.values
modeComparison.strong$rq.95 = fit.strong.rq.95$fitted.values

## fit median and quantiles to simulated data and add them to data.frames
fit.mut.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.mut, method = "fn")
fit.mut.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.mut, method = "fn")
fit.mut.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.mut, method = "fn")

modeComparison.mut$rq.5 = fit.mut.rq.5$fitted.values
modeComparison.mut$rq.05 = fit.mut.rq.05$fitted.values
modeComparison.mut$rq.95 = fit.mut.rq.95$fitted.values

## fit median and quantiles to experimental data
fit.exp.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.exp, method = "fn")
fit.exp.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.exp, method = "fn")
fit.exp.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.exp, method = "fn")

modeComparison.exp$rq.5 = fit.exp.rq.5$fitted.values
modeComparison.exp$rq.05 = fit.exp.rq.05$fitted.values
modeComparison.exp$rq.95 = fit.exp.rq.95$fitted.values

## put simulated and experimental data together

@@

```{r Pn-vs-mode-energy,cache = 2}
# plot Pn vs energy
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

@@

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin = Pn.median.min,ymax = Pn.median.max), size = .2, alpha = .4) +
    geom_line(aes(y = rq.5))  +
    labs(x = "mode energy", y = "structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
p.facet %+% subset(dat,dataset == "exp")
p.facet %+% subset(dat,dataset == "mut")
p.facet %+% subset(dat,dataset == "mut+sel")
p.facet
p + theme(legend.position = "bottom")

@@

```{r}
dat = modeComparison.all.datasets

#dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

@@

r.exp.mut = cor(dat.exp$Pn.median, dat.mut$Pn.median)
r.exp.strong = cor(dat.exp$Pn.median, dat.strong$Pn.median)
r.mut.strong = cor(dat.mut$Pn.median, dat.strong$Pn.median)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)
```
